ggalluvial: Layered Grammar for Alluvial Plots

### 2020-07-23 README.rmd
docs(readme,home): update branch descriptions from master to main

[![Travis](https://travis-ci.org/corybrunson/ggalluvial.svg?branch=master)](https://travis-ci.org/corybrunson/ggalluvial)
[![CRAN](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)

@@

The [cran branch](https://github.com/corybrunson/ggalluvial/tree/cran) will contain the version most recently submitted to [CRAN](https://cran.r-project.org/package=ggalluvial).

The development version can be installed from GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
Note that, in order to build the vignettes, the imported packages **alluvial**, **ggfittext**, and **ggrepel** must be installed. To skip this step, leave `build_vignettes` unspecified or set it to `FALSE`.

The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", ref = "optimization")
```
Note, however, that this branch has not kept pace with the `master` branch or with recent upgrades on CRAN.

@@

Contributions in any form are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated. See the [CONTRIBUTING](https://github.com/corybrunson/ggalluvial/blob/master/CONTRIBUTING.md) file for guidance, and please respect the [Code of Conduct](https://github.com/corybrunson/ggalluvial/blob/master/CODE_OF_CONDUCT.md).

>>>>

[![Travis](https://travis-ci.org/corybrunson/ggalluvial.svg?branch=main)](https://travis-ci.org/corybrunson/ggalluvial)
[![CRAN](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)

@@

The [`cran` branch](https://github.com/corybrunson/ggalluvial/tree/cran) will contain the version most recently submitted to [CRAN](https://cran.r-project.org/package=ggalluvial). It is duplicated in the `master` branch, from which source the [website](https://corybrunson.github.io/ggalluvial/) is built.

The development version can be installed from the (default) `main` branch on GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial@main", build_vignettes = TRUE)
```
Note that, in order to build the vignettes, the imported packages **alluvial**, **ggfittext**, and **ggrepel** must be installed. To skip this step, leave `build_vignettes` unspecified or set it to `FALSE`.

The
[`optimization` branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", ref = "optimization")
```
Note, however, that this branch has not kept pace with the `main` branch or with recent upgrades on CRAN.

@@

Contributions in any form are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated. See the [CONTRIBUTING](https://github.com/corybrunson/ggalluvial/blob/main/CONTRIBUTING.md) file for guidance, and please respect the [Code of Conduct](https://github.com/corybrunson/ggalluvial/blob/main/CODE_OF_CONDUCT.md).
